# An Overview of Norway: Top Recipients, Key Projects, and Areas for Collaboration 

The following sections provide an overview of Norway’s statistical activities including top ten country recipients alongside the active donors in those countries, and a comparison of Norway’s flagship projects with similar donor activities in that project’s country. This information provides insight for the development of Norway’s future data strategy as well as possible coordination and collaboration on existing and future statistical activities. 


``` {r map, echo = F, message = F, fig.cap = "Country-specific support for data and statistics by Norway (2018-2022)"}
library(highcharter)
library(maps)
library(dplyr)
source("code/00. boot.R")

df_map <- read_rds("Data/intermediate/80.3 temp Norway map.rds")
hcmap(
  map = "custom/world-highres3", # high resolution world map
  data = df_map, # name of dataset
  joinBy = "iso-a3",
  value = "disbursement",
  name = "Disbursements in 2017-2020 (USD)",
  # showInLegend = T, # hide legend
  # nullColor = "#DADADA",
  download_map_data = F
) %>%
  hc_mapNavigation(enabled = FALSE) %>% 
  hc_exporting(enabled = TRUE)

```

# Top Recipients of Statistical Support

In the last 3 years, 10 countries received more than $ 300K from Norway for data and statistics. Norway is also among the top six donors in all of them. Norway should consider to collaborate with other top 5 donors in these countries. 

``` {r other-donors, echo = FALSE, message = F}
library(kableExtra)
conflicted::conflict_prefer("group_rows", "kableExtra", "dplyr")
conflicted::conflict_prefer("filter","dplyr")
options(knitr.kable.NA = '')
source("code/00. boot.R")
options(kableExtra.html.bsTable = T)

# source("code/01. Norway_factsheet.R", echo = F, print.eval = F)
df_coordination_matrix <- read_rds("Data/intermediate/80.5 coordination matrix.rds")

df_coordination_matrix %>% 
  rename(Recipient = Recipient_Country, 
         `Disbursement (USD thousand)` = Disbursements_by_Norway,
         Ranking = Norway_ranking ) %>% 
  kbl(align = "c", 
      # df_coordination_matrix, 
      # col.names = gsub("[_]", " ", names(df_coordination_matrix)), 
      # booktabs = TRUE,
      caption = "Other top donors in countries received over $300K disbursements from Norway in 2018-2020"
  )  %>%  
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
  )  %>% 
  kable_styling(fixed_thead = T) %>%
  add_header_above(c(" ", "Norway" = 2, "Top 5 donors and their relevant disbursements v. Norway" = 5))%>%
  column_spec(c(1,3), border_right = T ) %>%
  scroll_box(width = "100%", box_css = "border: 0px;"
             , height = "600px") 


```

Out of these top donors, the United States, United Kingdom, Sweden, and Canada are the most active bilateral donors in Norway's top then recipients. A few lessons learned from their statistical support include:

* **United State:** The U.S is one of top ten donors of statistics from 2018-2020. ([PRESS 2022](https://www.oecd-ilibrary.org/sites/c3cfb353-en/1/4/1/index.html?itemId=/content/publication/c3cfb353-en&_csp_=281dfa109194f953c9d10eb236ea1a44&itemIGO=oecd&itemContentType=book#figure-d1e1538)) Health and population data are a key focus of US support. Over the years, the U.S has learned several lessons regarding its investments in statistics including: the importance of leveraging local data systems; a focus on data access and use at the local and subnational levels is key; the need for appropriate data governance structures that can balance a country’s expansion traditional and innovation sources with the need for interoperability, privacy, and data ethics; and the importance of investing in gender-balanced data efforts both in terms of collection and production but also data literacy and skills among women. ([OECD, Data for Development Profile](https://www.oecd-ilibrary.org/sites/84baa8f3-en/1/3/2/14/index.html?itemId=/content/publication/84baa8f3-en&_csp_=e37a72fa9d323403b8feae4f28b72657&itemIGO=oecd&itemContentType=book)) 

* **Canada:** Canada’s official development assistance (ODA) to data and statistics has a strong focus on gender equality and reproductive, maternal, newborn and child health, in line with its feminist international assistance policy. Their experience as a leading provider of statistical support over the years has generated several lessons. While smaller NSOs often have a great potential to scale and innovate, Canada found they may lack capacity to absorb the support due to human resources or technological constraints. Canada has also found that coordination among partners in the region is critical to leverage synergies and avoid duplication. Regional workshops that address common challenges can foster future collaboration and mutual assistance among participating countries, ensuring that support remains targeted and relevant to the region. Finally, regional programmes should encourage national statistical offices that excel in specific areas to develop further into regional centres of expertise, laying the foundations for future South-South co-operation. ([OECD, Data for Development Profile](https://www.oecd-ilibrary.org/sites/84baa8f3-en/1/3/2/14/index.html?itemId=/content/publication/84baa8f3-en&_csp_=e37a72fa9d323403b8feae4f28b72657&itemIGO=oecd&itemContentType=book)) 

* **Sweden:** Similar to the U.S, the Sweden is one of the top ten donors of statistics. ([PRESS 2022](https://www.oecd-ilibrary.org/sites/c3cfb353-en/1/4/1/index.html?itemId=/content/publication/c3cfb353-en&_csp_=281dfa109194f953c9d10eb236ea1a44&itemIGO=oecd&itemContentType=book#figure-d1e1538)) Sweden’s approach has primarily focused on long-term co-operation as most Statistics Sweden’s programmes have a duration of around eight to ten years. Experiences have confirmed that ensuring that support is in line with the countries’ own priorities and strategies is crucial to maintaining sustainability and to achieving long-lasting development of a statistical system.  Evaluations have highlighted the need for broad-based support of the system as a whole and explain their shift support from capacity to produce statistics on issues of user engagement, planning processes and the dissemination of statistics. The placement of an on-site advisor to support the partner organisation is a fundamental aspect of Statistics Sweden’s support in statistical development and appears to be a key success factor for more sustainable outcomes. ([OECD, Data for Development Profile](https://www.oecd-ilibrary.org/sites/84baa8f3-en/1/3/2/14/index.html?itemId=/content/publication/84baa8f3-en&_csp_=e37a72fa9d323403b8feae4f28b72657&itemIGO=oecd&itemContentType=book)) 


# Norway’s Key Projects and Complementary Activities by Other Donors

It is strongly recommended that the program managers of the following projects to coordinate with other donors, who are also funding large amount to same countries with similar sectoral focus.  


``` {r significant-overlaps, echo = FALSE, message = F}

# df_overlap_final <- read_rds("data/intermediate/80.2 temp norway overlap.rds")
df_overlap_final_long <- read_rds("Data/intermediate/80.3 temp Norway overlaps long.rds")
df_overlap_final_long_print <- read_rds("Data/intermediate/80.3 temp Norway overlaps long print.rds")
vec_norway_project <- read_rds("data/intermediate/80.3 temp Norway overlaps vec Norway rows.rds")
names(df_overlap_final_long_print) = gsub("[_]", " ", names(df_overlap_final_long_print))

kbl(df_overlap_final_long_print, align = "c",  
    caption = "Overlapping projects") %>%
  kable_paper("hover"
              , full_width = F
              # , font = "Cambria"
              ) %>%
  kable_styling(fixed_thead = T) %>%
  # column_spec(1, bold = T)   %>%
  column_spec(1:7, color = "black",
              background = spec_color(as.numeric(as.factor(df_overlap_final_long$norway_project_number)), end = 0.5, alpha = 0.5)) %>%
  row_spec(vec_norway_project,
           bold = T,
           #italic = T, underline = T,
           color = "white") %>%
  collapse_rows(columns = 1, valign = "top")%>%
  # kable_material(c("striped", "hover")) %>% 
  scroll_box(width = "100%", box_css = "border: 0px;"
             , height = "600px") 


```


# Key Projects by Donors in Norway’s Top Ten Recipient Countries 

In the ten countries which receive significant amount of support from Norway, programme managers should also consider other large programmes on data and statistics are listed below:



``` {r projectlist, echo = FALSE, message = F}
df_project_list <- read_rds("data/intermediate/80.4 project list.rds")
df_project_list %>%
  select(-`Long Description`) %>% 
  filter(`USD commitment` > 100000, 
         `Project title` != "") %>% 
  relocate(Gender,.after = last_col()) %>% 
  kbl(
    # df_project_list, 
    # col.names = gsub("[_]", " ", names(df_coordination_matrix)), 
    # booktabs = TRUE,
    caption = "Other large statistical projects in the countries where Norway is also active", 
    align = "c") %>% 
  kable_paper("hover", full_width  = F) %>% 
  kable_styling(fixed_thead = T
  )%>%
  scroll_box(width = "100%", box_css = "border: 0px;", height = "600px")

```

